First Season MWA EoR Power Spectrum Results at Redshift 7

### 2016-06-02 ms.tex
Minor edits for style consistency

Early in our analysis it became apparent that the bandpass of each MWA antenna requires 
more free parameters than those described in equation~\ref{eq:cal1}. In particular, differing 
beamformer to receiver cables lead to different bandpass shapes due to signal attenuation. 
We therefore allow the amplitude bandpass factor to depend on cable length, $B_{\alpha}
(\nu)$, where $\alpha$ denotes the cable type.\footnote{For logistical purposes the 
beamformer to receiver cables were installed in six set lengths. Cables of length 90, 150, 
and 230 meters are RG-6, while 320, 400, and 524 meter cables are LMR400-75.}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mwacs_ratio.pdf}
\caption{Power spectrum ratio difference, according to equation~\ref{eq:diff_ratio}. This 
metric shows the difference in the fractional E-W residual 2D power spectrum, comparing 
the MWACS catalog and our hierarchical catalog. By dividing the residual spectrum by the 
corresponding dirty spectrum before subtracting we remove the effect of the overall flux 
scale change due to differing calibration solutions. We see that the wedge is completely 
positive (higher fractional residual when using the MWACS catalog), confirming that the 
hierarchical catalog subtracts more power from the data. This also reassures that the 
calibration using the new catalog is more accurate. 
\label{fig:mwacs_ratio}
}
\end{figure}

@@

Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS 
pipeline successfully calibrated and included 1,003. The remainder failed to calibrate 
successfully, potentially due to adverse ionospheric conditions. The data were divided into the 
same three redshift bins, and the 2D and 1D power spectra formed. Table \ref{tbl:limits} 
displays comparison 2-sigma upper limits, demonstrating broad consistency between the 
pipelines. The RTS$+$CHIPS best limits appear at a lower $k$ bin than FHD$+$\eppsilon, 
owing to the different structure of the foreground leakage for the two pipelines. 
Figure~\ref{fig:slices}, which shows the resulting FHD$+$\eppsilon slices in $k_\parallel$ and 
$k_\bot$, also displays the equivalent power profiles for RTS$+$CHIPS. The comparison 
pipeline shows significantly more power at low $k_\bot$, consistent with no diffuse model 
being subtracted from the data. Aside from this area, the two pipelines show consistent 
results. Figure \ref{fig:ps_comparison} compares the 1D power from both pipelines for the 
three central redshifts studied in this work. The magenta line reproduces the FHD$+$\eppsilon 
results from Figure \ref{fig:1d_ps}, while the blue line plots the equivalent RTS$+$CHIPS 
results (with coarse band harmonics included). Despite the differences in the two pipelines, 
they produce consistent power across a range of scales, supporting the robustness of the 
results.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{1D_spectra_comparison.pdf}
\caption{
Here we compare the upper limits from the FHD$+$\eppsilon pipeline with those from the 
RTS$+$CHIPS pipeline. The magenta lines are repeated from Figure \ref{fig:1d_ps}, and the blue line
is the power plus two sigma thermal error bars line generated by CHIPS. CHIPS does not 
excise the coarse band harmonic lines, and so we see their strong effect where there are 
gaps in the magenta lines. The most notable differences are the ability of the RTS$+$CHIPS pipe
to access lower $k$ modes, while the FHD$+$\eppsilon pipe suppresses moe power before and
after the first coarse band harmonic. While the different analysis methods result in slightly
different upper limits, they are generally in agreement. 
\label{fig:ps_comparison}
}
\end{figure}

>>>>

Early in our analysis it became apparent that the bandpass of each MWA antenna requires 
more free parameters than those described in Equation~\ref{eq:cal1}. In particular, differing 
beamformer to receiver cables lead to different bandpass shapes due to signal attenuation. 
We therefore allow the amplitude bandpass factor to depend on cable length, $B_{\alpha}
(\nu)$, where $\alpha$ denotes the cable type.\footnote{For logistical purposes the 
beamformer to receiver cables were installed in six set lengths. Cables of length 90, 150, 
and 230 meters are RG-6, while 320, 400, and 524 meter cables are LMR400-75.}

@@

\begin{figure}
\includegraphics[width=\columnwidth]{mwacs_ratio.pdf}
\caption{Power spectrum ratio difference, according to Equation~\ref{eq:diff_ratio}. This 
metric shows the difference in the fractional E-W residual 2D power spectrum, comparing 
the MWACS catalog and our hierarchical catalog. By dividing the residual spectrum by the 
corresponding dirty spectrum before subtracting we remove the effect of the overall flux 
scale change due to differing calibration solutions. We see that the wedge is completely 
positive (higher fractional residual when using the MWACS catalog), confirming that the 
hierarchical catalog subtracts more power from the data. This also reassures that the 
calibration using the new catalog is more accurate. 
\label{fig:mwacs_ratio}
}
\end{figure}

@@

Of the 1,029 observations calibrated and used by the FHD pipeline, the RTS$+$CHIPS 
pipeline successfully calibrated and included 1,003. The remainder failed to calibrate 
successfully, potentially due to adverse ionospheric conditions. The data were divided into the 
same three redshift bins, and the 2D and 1D power spectra formed. Table \ref{tbl:limits} 
displays comparison 2-sigma upper limits, demonstrating broad consistency between the 
pipelines. The RTS$+$CHIPS best limits appear at a lower $k$ bin than FHD$+$\eppsilon, 
owing to the different structure of the foreground leakage for the two pipelines. 
Figure~\ref{fig:slices}, which shows the resulting FHD$+$\eppsilon slices in $k_\parallel$ and 
$k_\bot$, also displays the equivalent power profiles for RTS$+$CHIPS. The comparison 
pipeline shows significantly more power at low $k_\bot$, consistent with no diffuse model 
being subtracted from the data. Aside from this area, the two pipelines show consistent 
results. Figure~\ref{fig:ps_comparison} compares the 1D power from both pipelines for the 
three central redshifts studied in this work. The magenta line reproduces the FHD$+$\eppsilon 
results from Figure~\ref{fig:1d_ps}, while the blue line plots the equivalent RTS$+$CHIPS 
results (with coarse band harmonics included). Despite the differences in the two pipelines, 
they produce consistent power across a range of scales, supporting the robustness of the 
results.

@@

\begin{figure}
\includegraphics[width=\columnwidth]{1D_spectra_comparison.pdf}
\caption{
Here we compare the upper limits from the FHD$+$\eppsilon pipeline with those from the 
RTS$+$CHIPS pipeline. The magenta lines are repeated from Figure~\ref{fig:1d_ps}, and the blue line
is the power plus two sigma thermal error bars line generated by CHIPS. CHIPS does not 
excise the coarse band harmonic lines, and so we see their strong effect where there are 
gaps in the magenta lines. The most notable differences are the ability of the RTS$+$CHIPS pipe
to access lower $k$ modes, while the FHD$+$\eppsilon pipe suppresses moe power before and
after the first coarse band harmonic. While the different analysis methods result in slightly
different upper limits, they are generally in agreement. 
\label{fig:ps_comparison}
}
\end{figure}
